Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID

### 2024-01-23 outputs/paper/paper.qmd
initial final paper upload

---
title: "Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID"
subtitle: "Data Visualization in R"
author:
  - Francesca Ye
email: francesca.ye@mail.utoronto.ca
prerequisites: "Datasets taken from opensourcetoronto and can be found here: https://open.toronto.ca/catalogue/"
date: January 22 2024 
date-format: long
abstract: 
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID"
subtitle: "Data Visualization in R"
author:
  - Francesca Ye
email: francesca.ye@mail.utoronto.ca
prerequisites: "Datasets taken from opensourcetoronto and can be found here: https://open.toronto.ca/catalogue/"
date: January 22 2024 
date-format: long
abstract: "test"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
library(tinytex)
```
